### 2013-09-18 chi2014/abstract.tex
edits

Microtask marketplaces enable hybrid computational systems that use crowds to solve problems of creativity, such as brainstorming. We present a first characterization of brainstorming in this context, providing models for the rate of idea generation, the rate of category generation and the originality of generated ideas. We demonstrate that the rates of idea and category generation can be closely fit by a logarithmic model, and show that the first few responses of a brainstorming run are drawn from a pool of very common, obvious ideas. Our results suggest a cutoff for this strategy 20th idea. Furthermore, we explore the phenomenon of \emph{riffing} in brainstorming tasks, and replicate two related findings from prior work. Our results provide recommendations for those leveraging the crowd for brainstorming, and comparable models of creative idea generation research community.

>>>>

Microtask marketplaces enable hybrid computational systems that use crowds to solve problems of creativity, such as brainstorming. We present a first characterization of brainstorming in this context, providing models for the rate of idea generation, the rate of category generation, and the uniqueness of generated ideas. We demonstrate that the rates of idea and category generation can be closely fit with an exponential model. We also show that the first few responses of a brainstorming run are drawn from a pool of very common, obvious ideas, and become more original after 20 ideas have been produced by an individual. Our data also show support for the SIAM model (search for ideas in associative memory) \cite{nijstad_how_2006} in which workers draw ideas from a single category before moving on to a new category. Our results provide clear recommendations for practitioners and researchers alike who wish to leverage the crowd for brainstorming.
